\documentclass[10pt,a4paper,hidelinks]{article}
\usepackage[a4paper,margin=0.65in]{geometry}
\usepackage{mdwlist}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{xcolor}
\usepackage{scrextend}

% Font %
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\pagestyle{empty}

% indent section style
\newenvironment{indentsection}[1]%6
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% Colors
\definecolor{IFDarkGreen}{HTML}{40916C}
\definecolor{IFMediumGreen}{HTML}{74C69D}
\definecolor{IFLightGreen}{HTML}{B7E4C7}

\begin{document}

\begin{center}
\setstretch{1.2}{
{\huge \textbf{Tommaso Manzana}}

+39 3518881347\ \ \textbullet
\ \ manzana.tommaso@gmail.com 

\href{https://github.com/TommasoManzana}{github.com/TommasoManzana} \ \textbullet
\ \ \href{https://www.linkedin.com/in/tommaso-manzana/}{linkedin.com/in/tommaso-manzana}
\\
}
\end{center}

%\vspace{0.3em}


% -------------------- Education --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Education}}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Bachelor in Computer Science}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.unitn.it/}{\textbf{UniTn}}}{, Trento}}}
	\\
	\headerrow
		{\emph{Sep 2019 -- Jul 2023}}
		{\emph{}}

        \item 
	\headerrow
		{\textbf{Diploma in Scientific High School}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://liceorosmini.eu/}{\textbf{Liceo Rosmini}}}{, Rovereto}}}
	\\
	\headerrow
		{\emph{Sep 2013 -- Jun 2018}}
		{\emph{}}
        {
        \begin{addmargin}{6pt}{}
        \small{pathway: applied Sciences with \textbf{Computer Science}}
        \end{addmargin}
% 	\begin{itemize*}
% 	   % \setlength\itemsep{2pt}
% 		\item {Algorithms, Data Structures, Complexity Analysis, Compiler Design, OOP, Networking, Operating Systems, Computer Architecture, C/Python.}
% 	\end{itemize*}

\end{itemize}



% -------------------- Experience --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Experience}}


\renewcommand{\labelitemi}{$\bullet$}
% \renewcommand\labelitemii{$\--$}

\begin{itemize}
    \setstretch{0.75}
    \setlength\itemsep{5pt}
	\parskip=0.1em

    \item
	\headerrow
		{\textbf{Software Engineer (Full-Stack \& AI)}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://legconsulenze.it/}{\textbf{LEG s.r.l.}}}{, Brescia}}}
	\\
	\headerrow
		{\emph{Oct 2022 -- Present}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
		\item Designed and developed {\href{https://app.laorange.it/}{\textbf{SpiritOrange}}}, an \textbf{Ionic} app that recommends tailored cocktails based on user preferences, including ongoing implementation of \textbf{NLP} analysis on the cocktails' ingredients, flavour profile, and serving style.
		\item Developed {\href{https://backoffice.algorec.it/}{\textbf{Algorec}}} a credit platform that computes the profitability ranking of a property based on location, size, credit status and amenities. The platform uses \textbf{predictive modeling} to analyze real estate market trends and predict future profitability.
	\end{itemize*}

	\item
	\headerrow
		{\textbf{Full-Stack Developer}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.greenvulcano.com/}{\textbf{GreenVulcano}}}{, Rome}}}
	\\
	\headerrow
		{\emph{Dec 2021 -- Aug 2022}}
		{\emph{}}
	% TODO rewrite this
	\begin{itemize*}
	    \setlength\itemsep{2pt}
		\item Developed {\href{https://effatta.it/}{\textbf{Effatta}}}, App in \textbf{React Native} that uses \textbf{Robotic Process Automation} to manage electronic receipt via {\href{https://www.agenziaentrate.gov.it/portale/web/english}{\textbf{The Revenue Agency}}}'s API
		\item Developed {\href{https://www.facebook.com/CanticoVR360/}{\textbf{Cantico}}} , App in \textbf{React Native} to book theaters \& live-events
	\end{itemize*}
	
	\item
	\headerrow
		{{\href{https://www.fis-ski.com/en/international-ski-federation/news-multimedia/news-2022/ski-race-genie-the-first-live-fan-engagement-app-in-wintersports}{\textbf{Project Engineer}}}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.onesporter.com/en}{\textbf{OneSporter}}}{, Tarvisio}}}
	\\
	\headerrow
	    {\emph{Jun 2021 -- Mar 2022}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
	    \item Won {\href{https://pressroom.unitn.it/alfresco/download/workspace/SpacesStore/a1ed3d31-491d-4f20-95b3-ba1fc2f0f45b/cs\%20Hackathon\%20UniSport.pdf}{\textbf{Winter Sports Hackathon 2021}}} as part of a 4-member team hosted by {\href{https://www.unitn.it/}{\textbf{UniTn}}}.
	    \item Developed a game app in \textbf{Ionic} to play during live ski events.
	    \item Partnered with {\href{https://www.fis-ski.com/}{\textbf{FIS}}} to lunch the game, premiered in {\href{https://www.cortinaskiworldcup.com/D/472181/fis-ski-race-genie.php}{\textbf{Cortina 2022}}} \& {\href{https://www.fis-ski.com/en/international-ski-federation/news-multimedia/news-2022/fis-ski-race-genie-returns-to-the-world-cup-finals}{\textbf{Courchevel 2022}}}
	\end{itemize*}

	\item
	\headerrow
		{{\href{http://www.provinz.bz.it/politik-recht-aussenbeziehungen/europa/eu-foerderungen/efre-2014-2020.asp}{\textbf{Project Engineer}}}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.saidea.it/}{\textbf{Saidea}}}{, Trento}}}
	\\
	\headerrow
		{\emph{Jan 2021 -- Apr 2021}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
		\item Implemented a \textbf{Python} program to to manage 'Ticket' insertion on the company database (Antares).
		\item Coded a \textbf{PHP} script to extract solar panel data from Excel and load relationships into a database.
	\end{itemize*}
	
	\vspace{.1cm}
	
\end{itemize}


% -------------------- Projects --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Projects}}

	\begin{itemize}
 	\parskip=0.1em

 	\item
	\headerrow
		{\textbf{FST}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://falconeriskiteam.net/}{\textbf{Falconeri Ski Team}}}}}
	\\
	\headerrow
	    {\emph{Nov 2019 -- Present}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
	    \item As freelancers a college partner and I developed an \textbf{App} as well as a \textbf{Web App} for the purpose of managing a ski team, this was achieved through the  {\href{https://ionicframework.com/}{\textbf{Ionic}}} framework.
	    \item The front-end was implemented in \textbf{Angular} while the back-end was powered by Google's {\href{https://firebase.google.com/}{\textbf{Firebase}}}.
	\end{itemize*}
	
	\vspace{.1cm}
	
	\item
	\headerrow
            {{\href{https://www.manzana.it/finanza/login}{\textbf{Covid-19 Financial losses}}}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.manzana.it/}{\textbf{ManzanaIori}}}}}
	\\
	\headerrow
	    {\emph{Feb 2020 -- May 2020}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
	    \item Developed a WebApp to compute COVID-19 related financial losses, provided to the clients of an accountant studio. Data was taken from the accountant database and processed using \textbf{time series forecasting}, notably using \textbf{ARIMA}.
            \item The data would then be shown via interactive charts.
	\end{itemize*}
	
	\vspace{.1cm}

        \item
	\headerrow
            {{\href{https://github.com/TommasoManzana/ML-Galaxies-Classification-CNN/blob/main/I2ML_project_report_Tommaso_Manzana.pdf}{\textbf{Galaxies Classification CNN}}}}
		{\textbf{\colorbox{IFLightGreen!30}{\href{https://www.unitn.it/}{\textbf{UniTn}}}}}
	\\
	\headerrow
	    {\emph{Feb 2021 -- Jun 2021}}
		{\emph{}}
	\begin{itemize*}
	    \setlength\itemsep{2pt}
	    \item In the "Introduction to Machine Learning" university course I had to project an algorithm to classify images of galaxies. After using different approaches I settled with a \textbf{Convolutional NN} and \textbf{placed Top 20} among others in the final leaderboard.
            \item Most notably I fine-tuned a \textbf{Res-net 50} neural network in order to achieve the best accuracy.
	\end{itemize*}
	
	\vspace{.1cm}
	
\end{itemize}

% -------------------- Certifications --------------------

%{\color{IFMediumGreen} \hrule}
%\vspace{-0.3em}
%{\color{IFDarkGreen}\section*{Certifications}}
%
%\begin{itemize}
%	\parskip=0.1em
%
%	\item 
%	\headerrow
%		{\textbf{Certification 1}}
%		{{\href{https://www.example.com/}{\textbf{Certification}}}}
%	\\
%	\headerrow
%	    {\emph{\href{https://www.example.com/}{https://www.example.com/}}}
%		{\emph{}}
%	
%	\item 
%	\headerrow
%		{\textbf{Certification 2}}
%		{{\href{https://www.example.com/}{\textbf{Certification}}}}
%	\\
%	\headerrow
%	    {\emph{\href{https://www.example.com/}{https://www.example.com/}}}
%		{\emph{}}
%
%\end{itemize}


% -------------------- Languages --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Languages}}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{flushleft}
    \textbf{Italian} (Native), \textbf{English} (C1),  \textbf{Chinese} (B1), \textbf{German} (School-level)
\end{flushleft}
\end{indentsection}


% -------------------- Technical Skills --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Technical Skills}}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{flushleft}
   \textbf{Strong}: Python, PyTorch, TensorFlow, Angular, React, JavaScript, Node 
\end{flushleft}
\vspace{-1.0em}
\begin{flushleft}
   \textbf{Experienced}: PHP, NLTK, Spark, AWS, Git, SQL, C++, Flask
\end{flushleft}
\end{indentsection}


% -------------------- Personal --------------------

{\color{IFMediumGreen} \hrule}
\vspace{-0.3em}
{\color{IFDarkGreen}\section*{Personal \& Extracurricular}}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{flushleft}
At 24, I cultivate a wide range of interests that keep me engaged both mentally and physically. 

\begin{itemize*}
\setlength\itemsep{2pt}
    \item I am particularly keen on \textbf{sports}, I was a gymnast for the most part of my life and have participated in the Under-14 national competition. I am now practicing both climbing and biking.
    \item I am enthusiastic about \textbf{language learning} and I am currently striving to improve my proficiency in Chinese.
    \item As a teenager, I had the invaluable opportunity to \textbf{travel extensively}. Having visited more than 20 countries helped me to appreciate all the distinct facets of different cultures. Especially during middle school, I travelled to the UK on several occasions to learn the English language.
    \item Whilst not travelling I always endeavoured in \textbf{social activities} and contributed to my community, for more than 5 years I volunteered at local summer camps to entertain elementary school kids.
    \item Professionally speaking, I aspire to become a Machine Learning engineer.
\end{itemize*}

\end{flushleft}
\end{indentsection}

\end{document}